Supplementary Information: \nTree height, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2019-10-27 manuscript/climate_sensitivity_SI.Rmd
Updated SI with new file names

---
title: "Supplementary Information: \nTree height, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest"
author: "Ian McGregor, Ryan Helcoski, Norbert Kunert, Alan Tepley, Erika Gonzalez-Akre, Valentine Herrmann, Joseph Zailaa, Atticus Stovall, Norman Bourg?, William McShea?, Neil Pederson, Lawren Sack, Kristina Anderson-Teixeira"
output:
  pdf_document:
    fig_caption: yes
biblio-style: apalike
csl: apa.csl
header-includes:
- \usepackage{booktabs}
- \usepackage{dcolumn} #for sidewaystable
---

@@

### Supplementary Information
```{r, Table S1, eval=TRUE, echo=FALSE, message=FALSE}
library(knitr)
library(kableExtra)

heights <- read.csv("tables_figures/height_regression.csv", stringsAsFactors = FALSE)
kable(heights, booktabs=TRUE, format = "latex", caption = "Species-specific height regression equations") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

```{r, Table S2, eval=TRUE, echo=FALSE, message=FALSE}
tableS2 <- read.csv("tables_figures/candidate_traits.csv", stringsAsFactors = FALSE)
kable(tableS2, booktabs=TRUE, format = "latex", caption = "Candidate variables for best model") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

```{r, Plot, echo=FALSE, out.width='100%', fig.cap = "Map of ForestGEO plot", fig.pos='ht'}
  knitr::include_graphics("tables_figures/ForestGEO_plot.jpg")
```

*how do we want to present Table S3? Would it be better as an image of an excel file, since it's so large? Did we want to keep all coefficients here?*
```{r, Table S3, eval=TRUE, echo=FALSE, message=FALSE}
tableS3 <- read.csv("tables_figures/top_models_dAIC.csv", stringsAsFactors = FALSE)
kable(tableS3, booktabs=TRUE, format = "latex", caption = "Top model variations for each drought scenario, with dAICc values <= 2") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

![Location of cored trees](tables_figures/FigureS3.png){width=500px}

![Figure S1](tables_figures/FigureS1.png)
(see Issue #32)

>>>>

---
title: "Supplementary Information: \nTree height, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest"
author: "Ian McGregor, Ryan Helcoski, Norbert Kunert, Alan Tepley, Erika Gonzalez-Akre, Valentine Herrmann, Joseph Zailaa, Atticus Stovall, Norman Bourg?, William McShea?, Neil Pederson, Lawren Sack, Kristina Anderson-Teixeira"
output:
  pdf_document:
    fig_caption: yes
biblio-style: apalike
csl: apa.csl
header-includes:
- \usepackage{booktabs}
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
---

@@

### Supplementary Information
```{r Table S1, eval=TRUE, echo=FALSE, message=FALSE}
library(knitr)
library(kableExtra)

bark <- read.csv("tables_figures/tableS1_bark_regression.csv", stringsAsFactors = FALSE)
bark[,2] <- NULL
kable(bark, booktabs=TRUE, format = "latex", caption = "Table S1: Species-specific bark thickness regression equations") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

```{r Table S2, eval=TRUE, echo=FALSE, message=FALSE}
library(knitr)
library(kableExtra)

heights <- read.csv("tables_figures/tableS2_height_regression.csv", stringsAsFactors = FALSE)
heights[,2] <- NULL
kable(heights, booktabs=TRUE, format = "latex", caption = "Table S2: Species-specific height regression equations") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

```{r, Table S3, eval=TRUE, echo=FALSE, message=FALSE}
tableS3 <- read.csv("tables_figures/tableS3_candidate_traits.csv", stringsAsFactors = FALSE)
kable(tableS3, booktabs=TRUE, format = "latex", caption = "Table S3: Candidate variables for best model") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

```{r Figure S1, echo=FALSE, out.width='100%', fig.cap = "Figure S1: Map of ForestGEO plot", fig.pos='ht'}
  knitr::include_graphics("tables_figures/figureS1_ForestGEO_plot.jpg")
```

\newpage
*how do we want to present Table S4? Would it be better as an image of an excel file, since it's so large? Did we want to keep all coefficients here?*
```{r, Table S4, eval=TRUE, echo=FALSE, message=FALSE}
tableS4 <- read.csv("tables_figures/tableS4_top_models_dAIC.csv", stringsAsFactors = FALSE)
kable(tableS4, booktabs=TRUE, format = "latex", caption = "Table S4: Top model variations for each drought scenario, with dAICc values <= 2") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

![Figure S2: Location of cored trees](tables_figures/figureS2_location_cored_trees.png){width=500px}

\newpage
![Figure S3: Traits with TWI](tables_figures/figureS3_traits_with_twi.png)
(see Issue #32)
